Differentially Private Bayesian Inference

### 2018-03-29 main.tex
update sliding property of expomech

\begin{multline*}
\Delta_{l}u(x) = 
\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|\\
\max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in R\}}.
\end{multline*}

@@

Without loss of generality, we consider the case that $\Delta_{l}u(y) < \Delta_{l}u(x)$, $r = arg(\max\limits_{r' \in R}\{u(x,r')\}) = arg(\min\limits_{r' \in R}\{u(y,r')\})$ and $\Delta_{l}u(y) = u(x,r) - u(y,r)$. We have:
\begin{equation*}
\begin{split}
& \frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u(x)} 
+ \frac{\epsilon u(y,r')}{2 \Delta_{l}u(y)})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r)}{2 \Delta_{l}u(y)} 
+ \frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}\\
& > \frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon (u(x,r) + u(y,r'))}{2 \Delta_{l}u(x)})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon (u(y,r) + u(x,r'))}{2 \Delta_{l}u(y)})}\\
& > \frac
{|R|\ exp(\frac{\epsilon (u(x,r) + u(y,r))}{2 \Delta_{l}u(x)})}
{|R|\ exp(\frac{\epsilon (u(y,r) + u(x,r))}{2 \Delta_{l}u(y)})}\\
& = exp(\frac{\epsilon}{2} (\frac{u(x,r) + u(y,r)}{\Delta_{l}u(x)} - \frac{u(x,r) + u(y,r)}{\Delta_{l}u(y)})).
\end{split}
\end{equation*}

@@

% \twocolumn{
\begin{equation*}
\begin{split}
\hlg(
beta(\frac{n}{2} + 1, \frac{n}{2} + 1), 
beta(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1))
& <  \hlg(
beta(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1), 
beta(\frac{n}{2} + 1 + 2, \frac{n}{2} + 1 - 2))\\
\sqrt{1 - \frac{\betafun(
\frac{\frac{n}{2} + 1 + \frac{n}{2} + 1 + 1}{2},
\frac{\frac{n}{2} + 1 + \frac{n}{2} + 1 - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} + 1)
\betafun(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1)
}
}
}
& < \sqrt{1 - \frac{\betafun(
\frac{\frac{n}{2} + 1 + 1 + \frac{n}{2} + 1 + 2}{2}, 
\frac{\frac{n}{2} + 1 - 1 + \frac{n}{2} + 1 - 2}{2}, )}
{\sqrt{
\betafun(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1)
\betafun(\frac{n}{2} + 1 + 2, \frac{n}{2} + 1 - 2)
}
}
}\\
\sqrt{1 - \frac{\betafun(\frac{n + 3}{2},\frac{n + 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} + 1)
\betafun(\frac{n}{2} + 2, \frac{n}{2})
}
}
}
& < \sqrt{1 - \frac{\betafun(\frac{n + 5}{2}, \frac{n - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2, \frac{n}{2})
\betafun(\frac{n}{2} + 3, \frac{n}{2} - 1)
}
}
}\\
\frac{\betafun(\frac{n + 3}{2},\frac{n + 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} + 1)
\betafun(\frac{n}{2} + 2, \frac{n}{2})
}
}
& > \frac{\betafun(\frac{n + 5}{2}, \frac{n - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2, \frac{n}{2})
\betafun(\frac{n}{2} + 3, \frac{n}{2} - 1)
}
}\\
\frac{\betafun(\frac{n + 3}{2},\frac{n - 1}{2}) 
\frac{\frac{n - 1}{2}}{\frac{n - 1}{2} + \frac{n + 3}{2}}}
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} - 1) 
\frac{\frac{n}{2} - 1}{\frac{n}{2} - 1 + \frac{n}{2} + 1} 
\frac{\frac{n}{2}}{\frac{n}{2} + \frac{n}{2} + 1}}}
& > \frac{
\betafun(\frac{n + 3}{2}, \frac{n - 1}{2}) 
\frac{\frac{n + 3}{2}}{\frac{n + 3}{2} + \frac{n - 1}{2}} }
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} - 1) 
\frac{\frac{n}{2} + 1}{\frac{n}{2} + 1 + \frac{n}{2} - 1}
\frac{\frac{n}{2} + 2}{\frac{n}{2} + 2 + \frac{n}{2} - 1}}}\\
\frac{\frac{n - 1}{2}}{\sqrt{(\frac{n}{2} - 1)(\frac{n}{2})}}
& > \frac{\frac{n + 3}{2}}{\sqrt{(\frac{n}{2} + 1)(\frac{n}{2} + 2)}}\\
(n - 1) ^ 2 (n + 2)(n + 4)
& > (n + 3) ^ 2 n (n - 2)\\
n & > -1.
\end{split}
\end{equation*}

@@

\begin{footnotesize}
\begin{equation*}
\begin{split}
& \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})
\frac{n - 2m - 1}{n + 2m + 3}}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
\frac{n - 2m}{n + 2m + 2}
}
}\\
> & \frac{\betafun(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})
\frac{n - 2m - 3}{n + 2m + 5}}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
\frac{n - 2m - 2}{n + 2m + 6}
}
}\\
\end{split}
\end{equation*}

\begin{equation*}
\begin{split}
& \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}\\
> & \frac{\betafun(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}\\
\\
& \sqrt{1 - \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}}\\
< & \sqrt{1 - \frac{\betafun(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}}\\
\\
& \hlg(beta(\frac{n}{2} + 2 + m, \frac{n}{2} - m), beta(\frac{n}{2} + 3 + m, \frac{n}{2} - 1 - m))\\
< & \hlg(beta(\frac{n}{2} + m + 3, \frac{n}{2} - 1 - m), beta(\frac{n}{2} + m + 4, \frac{n}{2} - m - 2))\\
\end{split}
\end{equation*}
\end{footnotesize}

@@

\begin{equation*}
\underset{z \thicksim \expomech}{Pr}[u(r,x) = \hat{s}] \leq e^{\frac{\epsilon}{2}} \underset{z \thicksim \expomech}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2}
\end{equation*}

@@

\begin{proof}
\end{proof}

>>>>

\begin{equation*}
\Delta_{l}u(x) = 
\max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in R\}}.
\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|
\end{equation*}

@@

Without loss of generality, we consider the case that $\Delta_{l}u(y) < \Delta_{l}u(x)$, $r = arg(\max\limits_{r' \in R}\{u(x,r')\}) = arg(\min\limits_{r' \in R}\{u(y,r')\})$ and $\Delta_{l}u(y) = u(x,r) - u(y,r)$. We have:
\begin{equation*}
\begin{split}
\frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u(x)} 
+ \frac{\epsilon u(y,r')}{2 \Delta_{l}u(y)})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r)}{2 \Delta_{l}u(y)} 
+ \frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
& > \frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon (u(x,r) + u(y,r'))}{2 \Delta_{l}u(x)})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon (u(y,r) + u(x,r'))}{2 \Delta_{l}u(y)})}\\
& > \frac
{|R|\ exp(\frac{\epsilon (u(x,r) + u(y,r))}{2 \Delta_{l}u(x)})}
{|R|\ exp(\frac{\epsilon (u(y,r) + u(x,r))}{2 \Delta_{l}u(y)})}\\
& = exp(\frac{\epsilon}{2} (\frac{u(x,r) + u(y,r)}{\Delta_{l}u(x)} - \frac{u(x,r) + u(y,r)}{\Delta_{l}u(y)})).
\end{split}
\end{equation*}

@@

% \twocolumn{
\begin{small}
\begin{equation*}
\begin{split}
\hlg(
beta(\frac{n}{2} + 1, \frac{n}{2} + 1), 
beta(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1))
& <  \hlg(
beta(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1), 
beta(\frac{n}{2} + 1 + 2, \frac{n}{2} + 1 - 2))\\
\sqrt{1 - \frac{\betafun(
\frac{\frac{n}{2} + 1 + \frac{n}{2} + 1 + 1}{2},
\frac{\frac{n}{2} + 1 + \frac{n}{2} + 1 - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} + 1)
\betafun(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1)
}
}
}
& < \sqrt{1 - \frac{\betafun(
\frac{\frac{n}{2} + 1 + 1 + \frac{n}{2} + 1 + 2}{2}, 
\frac{\frac{n}{2} + 1 - 1 + \frac{n}{2} + 1 - 2}{2}, )}
{\sqrt{
\betafun(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1)
\betafun(\frac{n}{2} + 1 + 2, \frac{n}{2} + 1 - 2)
}
}
}\\
\sqrt{1 - \frac{\betafun(\frac{n + 3}{2},\frac{n + 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} + 1)
\betafun(\frac{n}{2} + 2, \frac{n}{2})
}
}
}
& < \sqrt{1 - \frac{\betafun(\frac{n + 5}{2}, \frac{n - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2, \frac{n}{2})
\betafun(\frac{n}{2} + 3, \frac{n}{2} - 1)
}
}
}\\
\frac{\betafun(\frac{n + 3}{2},\frac{n + 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} + 1)
\betafun(\frac{n}{2} + 2, \frac{n}{2})
}
}
& > \frac{\betafun(\frac{n + 5}{2}, \frac{n - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2, \frac{n}{2})
\betafun(\frac{n}{2} + 3, \frac{n}{2} - 1)
}
}\\
\frac{\betafun(\frac{n + 3}{2},\frac{n - 1}{2}) 
\frac{\frac{n - 1}{2}}{\frac{n - 1}{2} + \frac{n + 3}{2}}}
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} - 1) 
\frac{\frac{n}{2} - 1}{\frac{n}{2} - 1 + \frac{n}{2} + 1} 
\frac{\frac{n}{2}}{\frac{n}{2} + \frac{n}{2} + 1}}}
& > \frac{
\betafun(\frac{n + 3}{2}, \frac{n - 1}{2}) 
\frac{\frac{n + 3}{2}}{\frac{n + 3}{2} + \frac{n - 1}{2}} }
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} - 1) 
\frac{\frac{n}{2} + 1}{\frac{n}{2} + 1 + \frac{n}{2} - 1}
\frac{\frac{n}{2} + 2}{\frac{n}{2} + 2 + \frac{n}{2} - 1}}}\\
\frac{\frac{n - 1}{2}}{\sqrt{(\frac{n}{2} - 1)(\frac{n}{2})}}
& > \frac{\frac{n + 3}{2}}{\sqrt{(\frac{n}{2} + 1)(\frac{n}{2} + 2)}}\\
(n - 1) ^ 2 (n + 2)(n + 4)
& > (n + 3) ^ 2 n (n - 2)\\
n & > -1.
\end{split}
\end{equation*}
\end{small}

@@

\begin{small}
\begin{equation*}
\begin{split}
& \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})
\frac{n - 2m - 1}{n + 2m + 3}}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
\frac{n - 2m}{n + 2m + 2}
}
}\\
> & \frac{\betafun(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})
\frac{n - 2m - 3}{n + 2m + 5}}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
\frac{n - 2m - 2}{n + 2m + 6}
}
}\\
\end{split}
\end{equation*}

\begin{equation*}
\begin{split}
& \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}\\
> & \frac{\betafun(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}\\
\\
& \sqrt{1 - \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}}\\
< & \sqrt{1 - \frac{\betafun(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}}\\
\\
& \hlg(beta(\frac{n}{2} + 2 + m, \frac{n}{2} - m), beta(\frac{n}{2} + 3 + m, \frac{n}{2} - 1 - m))\\
< & \hlg(beta(\frac{n}{2} + m + 3, \frac{n}{2} - 1 - m), beta(\frac{n}{2} + m + 4, \frac{n}{2} - m - 2))\\
\end{split}
\end{equation*}
\end{small}

@@

\begin{equation*}
\underset{z \thicksim \expomech}{Pr}[u(r,x) = \hat{s}]
\leq
e^{\frac{\epsilon}{2}} \underset{z \thicksim \expomech}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2},
\end{equation*}
where the sensitivity in mechanism is smooth sensitivity $S(x)$, calculated by:
\begin{equation*}
S_{\beta}(x) = \max(\Delta_{l}u(x), \max_{y \neq x; y \in D^{n}}(\Delta_{l}u(y)\cdot e^{-\beta d(x,y)})),
\end{equation*}
where $\beta = \beta(\epsilon, \delta)$.

@@

\begin{proof}
We denote the normalizer of the probability mass in $\expomech$: $\sum_{r' \in \mathcal{R}}exp(\frac{\epsilon u(r',x)}{2 S(x)})$ as $NL_x$:
\begin{equation*}
\begin{split}
LHS 
  = \underset{z \thicksim \expomech}{Pr}[u(r,x) = \hat{s}]
& = \frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL_x}\\
& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta - \Delta)}{2 S(x)})}{NL_x}\\
& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)} + \frac{- \epsilon \Delta}{2 S(x)})}{NL_x}\\
& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL_x} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)})}.\\
\end{split}
\end{equation*}

By bounding the $\Delta \geq -S(x)$, we can get:

\begin{equation*}
\begin{split}
\frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL_x} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)}}
& \leq \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL_x} \cdot e^{\frac{\epsilon}{2}}\\
&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \expomech}{Pr}[u(r,x) = (\Delta + \hat{s})] \leq RHS\\
\end{split}
\end{equation*}
